---
title: 'Acquisition Opportunities and Challenges of Electronidex: Market Basket Analysis
  of Electronidex'
output:
  html_document:
    df_print: paged
  pdf_document: default
date: "2023-05-20"
---
# Subtitle: Unveiling Insights from Customer Purchase Patterns


## **R Markdown**

Students will continue to work as data analysts at Blackwell Electronics. Their job is to extend Blackwell's application of data mining methods to develop predictive models.

In this course, students will use the R statistical programming language augmented with machine learning packages to predict different product types a customer will be likely to buy. Next, students will create a recommender system that recommends additional purchases based on customer choices. Finally, students will present to management, explaining their insights and suggestions for data mining process improvements.

## Task 

Market Basket Analysis
Hi,

Blackwell Electronics' board of directors is considering acquiring Electronidex, a start-up electronics online retailer. The board of directors has asked us to help them better understand the clientele that Electronidex currently is serving and if it would be an optimal partnership.

They need our help to identify purchasing patterns that will provide insight into Electronidex's clientele. Attached is a CSV file that contains one month’s (30 days’ worth) of Electronidexes online transactions and a file containing all the electronics that they currently sell. Due to their lack of funding, Electronidex is only able to pull data on the items that customers purchased per their transactions.

I would like you to to use R to conduct a market basket analysis. You will be discovering any interesting relationships (or associations) between customer’s transactions and the item(s) they’ve purchased. These associations can then be used to drive sales-oriented initiatives such as recommender systems like the ones used by Amazon and other eCommerce sites. 

To help Blackwell’s board of directors form a clearer picture of Electronidex's customer buying patterns, please consider the following questions while you’re performing your analysis:

- **Are there any interesting patterns or item relationships within Electronidex's transactions?**
- **Would Blackwell benefit from selling any of Electronidex's items?**
- **In your opinion, should Blackwell acquire Electronidex?**
- **If Blackwell does acquire Electronidex, do you have any recommendations for Blackwell? (Ex: cross-selling items, sale promotions, should they remove items, etc.)**

Once you've completed your market basket analysis, please put together a formal business report in Word. Thank you in advance!

Best,

Danielle Sherman
Chief Technology Officer
Blackwell Electronics
www.blackwellelectronics.com

### Loading and installing required packages

```{r}
suppressPackageStartupMessages(library(arulesViz))
suppressPackageStartupMessages(library(arules))
suppressPackageStartupMessages(library(tidyverse))
library(readxl)
library(knitr)
library(ggplot2)
library(lubridate)
library(rmarkdown)
library(stringr)
library(RColorBrewer)
```

### Loading Datasets

```{r}
df_product <- read.csv("ElectronidexTransactions2017.csv", header = FALSE, sep = ",")
product <- read.transactions("ElectronidexTransactions2017.csv", format = "basket", sep = ",")
blackwellold <- read.csv("existingproductattributes2017.csv")
blackwellnew <- read.csv("newproductattributes2017.csv")
Product_Equivalence <- read.csv("product.csv", header = TRUE, sep = ";")
```




NOTE: 

- **ElectronidexTransactions.csv, is a record of one month’s (30 days’ worth) of 9835 online transactions and which items were purchased out of the 125 products Electronidex sells.**

- **The file, product.csv, is an equivalence list between the Product and Category sold by Electronidex, with 125 products that Electronidex sells broken down into 17 product types.**


### Equivalence dataframe

```{r}

equivalence <- data.frame(
  Category_Blackwell = c(
    "NULL", "PC & Laptop & Netbook", "Accessories", "Software", "Display", "Printer",
    "Printer Supplies", "Extended Warranty", "Tablet", "Smartphone", "Game Console", "NULL",
    "NULL", "NULL", "NULL", "NULL"
  ),
  Category_Electronidex = c(
    "Desktop", "Laptop",
    "Accessories, Computer Stands, Mouse and Keyboard Combo, Computer Cords, Computer Mice, Keyboard",
    "NULL", "Monitors", "Printer", "Printer Ink", "NULL", "Computer Tablets", "NULL",
    "NULL", "Speakers", "External Hard Drives", "Smart Home Devices",
    "Computer Headphones", "Active Headphones"
  )
)
equivalence

```



Comment: 

- This **equivalence** table serves as a guidethrough to understand the categories present in Blackwell's category potfolio
which are also present in Electronidex. They are several categoriws which are NULL, which means that they do not have a correspondent equivalent, these are values in which the category is present in one of the stores but not on the other and viceversa. 

# Categories present in Blackwell:

- 1. PC & Laptop = Laptop
- 3. Accessories
- 4. Software
- 5. Display
- 6. Printer
- 7. Printer Supplies
- 8. Extended Warranty
- 9. Netbook
- 10. Tablet
- 11. Smartphone
- 12. Game Console

# Categories present in Electronidex:

- 1. Desktop
- 2. Laptop
- 3. Monitors
- 4. Computer Mice
- 5. Keyboard
- 6. Mouse and Keyboard Combo
- 7. Computer Headphones
- 8. Active Headphones
- 9. Computer Cords
- 10. Accessories
- 11. Speakers
- 12. Printers
- 13. Printer Ink
- 14. Computer Stands
- 15. Computer Tablets
- 16. External Hard Drives
- 17. Smart Home Devices

# Preprocessing

```{r}
# Create an empty dataframe for df_copy

df_category <- data.frame(matrix(nrow = nrow(Product_Equivalence), ncol = ncol(Product_Equivalence)))
```


```{r echo = T, results = 'hide'}

# Create an empty dataframe df_category with the same dimensions as df_product
df_category <- data.frame(matrix(nrow = nrow(df_product), ncol = ncol(df_product)))

# Loop through the indices of df_product
#for (i in 1:nrow(df_product)) {
#  try({
#    for (e in 1:ncol(df_product)) {
#      print(i)
#      if (nchar(str_trim(df_product[i, e])) == 0) {
#        df_category[i, e] <- df_product[i, e]
#      } else {
#        df_category[i, e] <- Product_Equivalence[which(Product_Equivalence$producto == str_trim(df_product[i, e])), 1]
#        print(str_trim(df_product[i, e]))
#        print(Product_Equivalence[which(Product_Equivalence$producto == str_trim(df_product[i, e])), 1])
#      }
#    }
#  })
#}

```




```{r}
#Write df_copy to a CSV file
#write.csv(df_category, "category.csv", row.names = FALSE)

# Read transactions from the CSV file into category
df_category <- read.csv("category.csv", sep = ",")
category <- read.transactions("category.csv", format = "basket", sep = ",")

```

COMMENT:

Based on the information above:

- df represents the data in the file "ElectronidexTransactions.csv". It contains records of 9835 online transactions that occurred over a period of 30 days. Each transaction entry includes information about the purchased items from the 125 products sold by Electronidex.

- dfproduct represents the data in the file "product.csv". It is an equivalence list that maps the products sold by Electronidex to their respective categories. It contains 125 rows, each representing a product, and includes information about the category to which each product belongs. The categories are broken down into 17 product types.

**The purpose of the code is to create a copy of the df dataframe named df_copy with corresponding category information from dfproduct.** The code iterates over each row and column of df, checks if the value in df is empty, and if not, searches for the matching product in dfproduct. It then assigns the corresponding category value from dfproduct to the df_copy dataframe.

**This code essentially enhances the df dataframe by including the category information from dfproduct, providing a more comprehensive representation of the transactions with the corresponding product categories.**


# Exploratory Data Analysis Category - Using the arules and arulesviz package. 

```{r}
# Exploratory Data Analysis (EDA) - category

# View the transactions in category

#inspect(category)

# Check the number of transactions
length(category)  # 9836 Number of transactions.

# Check the number of items per transaction
#size(category)  # Number of items per transaction

# List the transactions by conversion (LIST must be capitalized)
#LIST(category)

# View the item labels
#itemLabels(category)

# Summary statistics of the category
#summary(category)

# Item frequency plot for the category

itemFrequencyPlot(category, topN = 17, type = "absolute", col = brewer.pal(8, 'Pastel2'), main = "Absolute Item Frequency for Category")

category

```


```{r}
# Exploratory Data Analysis (EDA) - product

# View the transactions in product

#inspect(product)

# Check the number of transactions
length(product)  # 9836 Number of transactions.

# Check the number of items per transaction
#size(product)  # Number of items per transaction

# List the transactions by conversion (LIST must be capitalized)
#LIST(product)

# View the item labels
#itemLabels(product)

# Summary statistics of the product
#summary(product)

# Item frequency plot for the product
if (!require("RColorBrewer")) {
  install.packages("RColorBrewer")
  library(RColorBrewer)
}
itemFrequencyPlot(product, topN = 30, type = "absolute", col = brewer.pal(8, 'Pastel2'), main = "Absolute Item Frequency for Product")

```
```{r}
rules_cat <- apriori(category, parameter = list(supp=0.005, conf=0.5))
rules_cat<- subset(rules_cat, lift > 1)
rules_cat <- sort(rules_cat, by='supp', decreasing = TRUE)
rules_cat <- rules_cat[!is.redundant(rules_cat)] 
gi <- generatingItemsets(rules_cat)
d <- which(duplicated(gi))
rules_cat<-rules_cat[-d]
summary(rules_cat)

plot(rules_cat, measure = c("support", "confidence"), shading = "lift")

```
```{r}
topRules <- rules_cat[1:5]
plot(topRules, jitter=0)
plot(head(sort(topRules, by = "lift")), method = "graph")
plot(topRules, method="grouped")
plot(topRules)
inspectDT(topRules)
```


```{r}

rules_prod <- apriori(product, parameter = list(supp=0.01, conf=0.25))
rules_prod <- subset(rules_prod, lift > 1)
rules_prod <- sort(rules_prod, by='lift', decreasing = TRUE)
rules_prod <- rules_prod[!is.redundant(rules_prod)] 
summary(rules_prod)
gi <- generatingItemsets(rules_prod)
d <- which(duplicated(gi))
rules_prod <-rules_prod[-d]
summary(rules_prod)

plot(rules_prod, measure = c("support", "confidence"), shading = "lift")

```
```{r}

topRules <- rules_prod[1:9]
plot(topRules, jitter=0)
plot(head(sort(topRules, by = "lift"), 22), method = "graph")
plot(topRules, method="grouped")
plot(topRules)


```


``` {r}

inspectDT(rules_prod)

```
``` {r}

Cat_Rules1 <- subset(rules_cat, items %in% "desktop")
CatRules1 <- sort(Cat_Rules1, by = "support", decreasing = TRUE)
top5_categories <- head(CatRules1, 5)
head(top5_categories)
plot(top5_categories)
inspectDT(top5_categories)



```


COMMENT:

**Desktop is the most popular category bought in Electronidex by far.**

**A staggering 20% of transactions are from people who buy a laptop and then a desktop**

**This is closely followed by a 17% of people who buy a monitor which will then also buy a desktop**


``` {r}

Cat_Rules2 <- subset(rules_cat, items %in% "laptop")
CatRules2 <- sort(Cat_Rules2, by = "support", decreasing = TRUE)
top5_categories <- head(CatRules2, 5)
head(top5_categories)
plot(top5_categories)
inspectDT(top5_categories)

```

Comment:

**Laptop is the second most bought category. 
It is interesting to note that 15% of the purchases include buying a monitor which turns into buying a laptop.**

**This is closely followed by a 12%  who buy a computer mice which will then also buy a laptop**

``` {r}

Cat_Rules3 <- subset(rules_cat, items %in% "monitors")
CatRules3 <- sort(Cat_Rules3, by = "support", decreasing = TRUE)
top5_categories <- head(CatRules3, 5)
head(top5_categories)
plot(top5_categories)
inspectDT(top5_categories)

```
Comment:

- **Monitors is the third most bought category.**

- It is interesting to note that 10% of the purchases include buying a computer mice will also buy a monitorwhich turns into buying a laptop.

- This is closely followed by a 9%  who buy a keyboard which will then also buy a laptop

``` {r}

rules_product <- apriori(product, parameter = list(support = 0.01, confidence = 0.5))
sorted_rules <- sort(rules_product, by = "support", decreasing = TRUE)
sorted_rules
top5_products <- head(sorted_rules, 5)
head(top5_products)
plot(top5_products)
inspectDT(top5_products)

```

``` {r}

Item_Rules<- subset(rules_product, items %in% "iMac")
ItemRules <- sort(Item_Rules, by = "support", decreasing = TRUE)
top5_products <- head(ItemRules, 5)
head(top5_products)
plot(top5_products)
inspectDT(top5_products)

```
``` {r}

Item_Rules1<- subset(rules_product, items %in% "HP Laptop")
ItemRules1 <- sort(Item_Rules1, by = "support", decreasing = TRUE)
top5_products <- head(ItemRules1, 5)
head(top5_products)
plot(top5_products)
inspectDT(top5_products)

```
``` {r}

Item_Rules2<- subset(rules_product, items %in% "CYBERPOWER Gamer Desktop")
ItemRules2 <- sort(Item_Rules2, by = "support", decreasing = TRUE)
top5_products <- head(ItemRules2, 5)
head(top5_products)
plot(top5_products)
inspectDT(top5_products)

```

#2.Would Blackwell benefit from buying Electronidex?

``` {r}


ItemRules3 <- subset(rules_cat, items %in% "Speakers")
sorted_ItemRules3<- sort(ItemRules3, by = "support", decreasing = TRUE)
top5_Speakers <- head(sorted_ItemRules3, 5)
head(top5_Speakers)
plot(top5_Speakers)
inspectDT(top5_Speakers)

ItemRules4 <- subset(rules_cat, items %in% "External Hardrives")
sorted_ItemRules4<- sort(ItemRules4, by = "support", decreasing = TRUE)
top5_External_Hardrives <- head(sorted_ItemRules4, 5)
head(top5_External_Hardrives)
plot(top5_External_Hardrives)
inspectDT(top5_External_Hardrives)
```


unique(df_new)

``` {r}
categories_dict <- c("laptop" = 1650, "desktop" = 1750, "monitors" = 300, "Computer Tablets" = 500, "Computer Mice" = 80, "Keyboard" = 300, 
                     "Mouse and Keyboard Combo" = 400, "Active Headphones" = 100, "Computer Headphones" = 150, "Computer Cords" = 30, 
                     "Computer Stands" = 60, "Accessories" = 70, "Speakers" = 200, "Printers" = 100, "Printer Ink" = 30, 
                     "External Hardrives" = 120, "Smart Home Devices" = 50)


df_category$Average_Price_Category_Transaction <- NA  # Create an empty "Category" column

# Iterate through each row and replace "Category" values based on matching keys in categories_dict
for (i in 1:nrow(df_category)) {
  categories <- unique(unlist(df_category[i,]))
  categories <- categories[!is.na(categories) & categories %in% names(categories_dict)]
  if (length(categories) > 0) {
    df_category$Average_Price_Category_Transaction[i] <- sum(categories_dict[categories])
  }
}

df_category$Average_Price_Category <- rowSums(df_category[, "Average_Price_Category_Transaction", drop = FALSE], na.rm = TRUE)  # Calculate the row sum for the "Category" column

df_category$Average_Price_Category_Transaction <- as.numeric(as.character(df_category$Average_Price_Category_Transaction))

df_category <- na.omit(df_category)
``` 

``` {r}
summary(df_category$Average_Price_Category_Transaction)
hist(df_category$Average_Price_Category_Transaction)
``` 
``` {r}

# Initialize the Pricing Strategy column
df_category$Range <- ""

# Set the threshold for transactions made by companies

# Assign the pricing strategy categories based on the price values and transaction type
df_category$Range[df_category$Range < 30] <- "Very Low Price (Light)"

df_category$Range[df_category$Average_Price_Category_Transaction >= 30 & df_category$Average_Price_Category_Transaction < 150] <- "Low"

df_category$Range[df_category$Average_Price_Category_Transaction >= 150 & df_category$Average_Price_Category_Transaction < 500] <- "Standard"

df_category$Range[df_category$Average_Price_Category_Transaction >= 500 & df_category$Average_Price_Category_Transaction < 1250] <- "Mid-High Price"

df_category$Range[df_category$Average_Price_Category_Transaction >= 1250 & df_category$Average_Price_Category_Transaction < 2000] <- "High Price"

df_category$Range[df_category$Average_Price_Category_Transaction >= 2000 & df_category$Average_Price_Category_Transaction < 3000] <- "Premium"

df_category$Range[df_category$Average_Price_Category_Transaction >= 3000] <- "B2B"

``` 



``` {r}
# Count the frequency of each range category
range_counts <- table(df_category$Range)

# Sort the range_counts in descending order
range_counts <- sort(range_counts, decreasing = TRUE)

# Create a vertical bar plot with ordered categories
barplot(range_counts, main = "Range Distribution", xlab = "Range", ylab = "Count", col = "steelblue", ylim = c(0, max(range_counts)))

# Calculate the percentage of each range category
percentage <- round((range_counts / sum(range_counts)) * 100, 1)

# Create a cross-tabulation table with percentages
cross_tab <- prop.table(range_counts) * 100
cross_tab <- round(cross_tab, 1)

# Print the cross-tabulation table
cat("\nCross-Tabulation of Range with Percentages:\n")
print(cross_tab)
``` 





``` {r}
# df_category$Rules <- "Other"
# 
# for (i in 1:nrow(df_product)) {
#   if (sum(grepl("Laptop", df_product[i, ]) | grepl("Desktop", df_product[i, ]) | grepl("Monitor", df_product[i, ]) |
#           grepl("Keyboard", df_product[i, ]) | grepl("Computer Mice", df_product[i, ]) | grepl("Computer Cords", df_product[i, ]) |
#           grepl("Mouse and Keyboard Combo", df_product[i, ]) | grepl("Computer Headphones", df_product[i, ]) |
#           grepl("Active Headphones", df_product[i, ]) | grepl("Speakers", df_product[i, ]) | grepl("Printers", df_product[i, ]) |
#           grepl("Printer Ink", df_product[i, ]) | grepl("Computer Stands", df_product[i, ]) | grepl("Computer Tablets", df_product[i, ]) |
#           grepl("External Hardrives", df_product[i, ]) | grepl("Smart Home Devices", df_product[i, ])) >= 4) {
#     df_product$Rules[i] <- "Office"
#   }
# }


# for (i in 1:nrow(df_)) {
#   if (sum(
#     grepl("Keyboard", df_product[i,]) |
#     grepl("Computer Mice", df_product[i,]) |
#     grepl("Computer Cords", df_product[i,]) |
#     grepl("Mouse and Keyboard Combo", df_product[i,]) |
#     grepl("Computer Headphones", df_product[i,]) |
#     grepl("Active Headphones", df_product[i,]) |
#     grepl("Speakers", df_product[i,]) |
#     grepl("Printers", df_product[i,]) |
#     grepl("Printer Ink", df_product[i,]) |
#     grepl("Computer Stands", df_product[i,]) |
#     grepl("Computer Tablets", df_product[i,]) |
#     grepl("External Hardrives", df_product[i,]) |
#     grepl("Smart Home Devices", df_product[i,]) |
#     grepl("monitors", df_product[i,])
#   ) >= 1) {
#     df_product$Rules[i] <- "Casual Buyers"
#   }
# }

# for (i in 1:nrow(df_product)) {
#   if (sum(grepl("Laptop", df_product[i,]) | grepl("Desktop", df_product[i,])>= 1) {
#     df_product$Rules[i] <- "Computer"
#   }
# }

```

``` {r}

# # Count the frequency of each range category
# range_counts <- table(df_product$Rules)
# 
# # Sort the range_counts in descending order
# range_counts <- sort(range_counts, decreasing = TRUE)
# 
# # Create a vertical bar plot with ordered categories
# barplot(range_counts, main = "Range Distribution", xlab = "Range", ylab = "Count", col = "steelblue", ylim = c(0, max(range_counts)))
# 
# # Calculate the percentage of each range category
# percentage <- round((range_counts / sum(range_counts)) * 100, 1)
# 
# # Create a cross-tabulation table with percentages
# cross_tab <- prop.table(range_counts) * 100
# cross_tab <- round(cross_tab, 1)
# 
# # Print the cross-tabulation table
# cat("\nCross-Tabulation of Range with Percentages:\n")
# print(cross_tab)
```

``` {r}

```

``` {r}

```

``` {r}

```

``` {r}

```

``` {r}

```

``` {r}

```


``` {r}

```










